Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots

### 2021-12-04 energy-planning.tex
polishing and fixes

%% author names and affiliations
\author{
  Adam Seewald$^{\text{1}}$, Hector Garcia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{1}}$, and Ulrik Pagh Schultz$^{\text{1}}$
  %\thanks{This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).}
  \thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
  \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
  \thanks{$^{\text{1}}$A. S., H. S. M., and U. P. S. are with the Unmanned Aerial Systems Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense. Email: {\tt\footnotesize ads@mmmi.sdu.dk};} 
  \thanks{$^{\text{2}}$H. G. is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Computense de Madrid, Spain.}
  \thanks{Digital Object Identifier (DOI): see top of this page.}
}

@@

\begin{abstract}
  The paper presents a planning algorithm for autonomous UAVs with energy constraints and solves the problem of dynamic planning of the path and computations simultaneously. The planning strategy is based on a periodic energy model that is empirically motivated and formally proved. The model is enhanced with the time and energy contribution of the path and computations. The algorithm replans both in function of the battery state accounting for uncertainty. The dynamic planning allows to exploit all the available resources, yet avoid possible in-flight failure in case of unexpected battery drops due to, e.g., adverse atmospheric conditions.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}  %
\label{sec:intro}       %
                        %
\IEEEPARstart{U}{se cases} involving aerial robots span broadly. They compromise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. A typical instance is an aerial robot visiting each point in a given space~\cite{cabreira2019survey}, running some on-board computational tasks, a problem in the literature under coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}. Here, the aerial robot might detect ground patterns and notify other ground-based actors with little human interaction (see Figure~\ref{fig:il-abs}). Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, damage prevention aerial robots~\cite{puri2017agriculture, daponte2019review}. In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}. We refer to computational tasks that can be scheduled with an energy impact as computations. We are interested in the simultaneous energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware planning-scheduling. Generic mobile robotics studies that deal with planning-scheduling energy awareness are scarce~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled} and focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled,ho2019learning}. Yet, aerial robots are particularly affected by various energy considerations. Indeed it would be generally required to land to recharge the battery~\cite{zamanakos2020energy}. Such a state of practice has prompted us to propose a planning-scheduling approach for autonomous aerial robots. It combines the past body of knowledge, addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints. Numerical simulations and experimental data of both static and dynamic plans-schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures. Figure~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies full plan-schedule~(\ref{sth:i}), that is optimized w.r.t. the battery~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defect~(\ref{sth:iii}).

\begin{figure}[t]
  \centering
  \vspace*{-6.5ex}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,0)
        {\scriptsize \input{\figpath/new/il_abs.tikz}};
    \node[inner sep=0pt] () at (-2,-5.67)
        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
    \node[inner sep=0pt] () at (2.1,-5.67)
        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
  \end{tikzpicture}
  \caption{An illustrative example of planning-scheduling. An initial plan~(in~\ref{sth:i}) is re-planned in-flight computations-wise~(in~\ref{sth:ii}) and motion-wise~(in~\ref{sth:iii}). Follow the collected energy data of a physical aerial robot flying the use case.}
  \label{fig:il-abs}
  \vspace*{-4.5ex}
\end{figure}

@@

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers forward thrust, and control surfaces maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations and vice-versa. The occurrence happens frequently with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2018towards,ho2019learning,ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.

To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (e.g., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc). Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}. Both the variations trajectories are derived for future time instants employing computations and motion energies and battery models. The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}. The motion wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of various plans-schedules. In Figure~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the motion energy model: the evolution is periodic, an observation we exploit in the energy models for the computations, motion, and battery models in Section~\ref{sec:energy-model}.

The remaining sections of the letter are then organized as follows. Section~\ref{sec:prob} provides basic constructs. These include the concepts of %computations and motion energies, 
plan, stages, triggering and final points, and path functions, as well as the problem formulation. Section~\ref{sec:algo} describes in detail the planning-scheduling. Section~\ref{sec:experimental} presents the results and showcases the performances, and Section~\ref{sec:conclusion} concludes and provides future perspectives. Appendices provide supplementary information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Formulation}  %
\label{sec:prob}               %
                               %
\begin{figure}[t]
  \footnotesize
  \begin{minipage}[l]{0.35\columnwidth}
    \caption{Definitions \ref{def:plan}--\ref{def:trigs} on a slice of the plan $\Gamma$. $\mathbf{p}_{\Gamma_1},\dots$ are triggering points, in which proximity happens change of stages $\Gamma_1,\dots$. Each contains a path function $\varphi_1,\dots$ and parameters to alter the path and schedule $c_{1,1},\dots$.}
    \label{fig:traj1}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.6\columnwidth}
    \centering
    \vspace*{-4.5ex}
    \input{\figpath/new/traj1.tikz}
  \end{minipage}
  \vspace*{-3.5ex}
\end{figure}

Before defining the problem of energy-aware planning-scheduling in Section~\ref{sec:pbfor}, Section~\ref{sec:prelim} provides necessary preliminaries. For CPP and, e.g., pattern detections in the agricultural use case, we assume that aerial robot travels a \emph{plan} with information about the path and the schedule.

%---

\subsection{Preliminaries}
\label{sec:prelim}

@@

Here, $\Gamma_i$ are \emph{stages}, and $\mathbb{Z}$ indicates the set of integers. At each stage, the aerial robot travels a path and runs a schedule on the computing hardware. Both are to be altered in Section~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}. $\varepsilon_i$ is a stage-dependent value detailed %along with $\mathbf{p}_{\Gamma_i}$ in and 
after Definition~\ref{def:trigs}.

\begin{defn}[Stage]\label{def:stage}
  The $i$th \emph{stage} $\Gamma_i$ at time instant $t$ of a plan $\Gamma$ is
  \begin{equation*}\begin{split}
    \Gamma_i:=\{\varphi_i(\mathbf{p}(t),c_i^\rho),c_i^\sigma\mid
    \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
      &\forall k\in[\sigma]_{>0},\,c_{i,\rho+k}\in\mathcal{S}_{i,k}\,\},
  \end{split}\end{equation*}
  where $c_i^\rho$ and $c_i^\sigma$ are $\rho$ \emph{path} and $\sigma$ \emph{computations parameters}. $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
\end{defn}

@@

The function $\varphi_i$ is the \emph{path function}, specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels the motion for the coverage. The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ indicates the upper/lower bound of a parameter $\cdot\,$, i.e.,
\begin{equation}
  \underline{\,\cdot\,}\leq\,\cdot\,\leq\overline{\,\cdot\,}.
\end{equation}

\begin{defn}[Path functions]
  \label{def:paths}
  $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}%\,\forall i\in\{1,2,\dots\}
  $ are \emph{path functions}, forming the path. They are a function of $\mathbf{p}(t)$ and path parameters $c_i^\rho(t)$ and are continuous and twice differentiable.
\end{defn}

@@

The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Definition~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.

Figure \ref{fig:traj1} illustrates the concepts in Definitions~\ref{def:plan}--\ref{def:trigs}. $\varphi_1,\dots,\varphi_6$ are path functions. $\varphi_1$ and $\varphi_5$ are circles, while $\varphi_2$, $\varphi_4$, and $\varphi_6$ are lines. They are all relative to different stages $\Gamma_1,\Gamma_2,\dots$. The constraint sets $\mathcal{C}_{1,1},\mathcal{C}_{2,1},\dots$ forms the area where it is possible to alter the paths $\varphi_1,\varphi_2,\dots$ with the parameters $c_{1,1},c_{2,1},\dots$; the gray area in the figure. The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.

@@

\begin{figure}[h!]
  \center
  \vspace*{-2.2ex}
  \begin{tikzpicture}[shorten >=.5pt,node distance=12.5ex,on grid,auto,initial text=\hspace*{-3ex}\footnotesize{$\Gamma_0$}]
    \footnotesize
    \node[state,initial] (q_i) {$\Gamma_1$}; 
    \node[state] (q_2) [right=of q_i] {$\Gamma_2$}; 
    \node        [right=of q_2] (q_dots0) {$\cdots$};
    \node[state] (q_0) [right=of q_dots0] {$\Gamma_n$};
    \node[state,accepting] (q_f) [right=of q_0] {$\Gamma_f$};
    \path[->]
    (q_i) edge node {$\mathbf{p}_{\Gamma_{1}}$} (q_2)
    (q_2) edge node {$\mathbf{p}_{\Gamma_{2}}$} (q_dots0)
    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{n-1}}$} (q_0)
    (q_0) edge [bend right=65] node [above] {$\mathbf{p}_{\Gamma_n}$} (q_i)
    (q_i) edge [bend left=-65] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
    (q_2) edge [bend left=-45] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
    (q_0) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
    (q_i) edge [loop above] node {$\mathbf{p}(t_1)$} (q_i)
    (q_2) edge [loop above] node {$\mathbf{p}(t_2)$} (q_2)
    (q_0) edge [loop above] node {$\mathbf{p}(t_3)$} (q_0)
    (q_f) edge [loop above] node {$\mathbf{p}(t_4)$} (q_f)
    ; %end path 
    %\draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=47pt},yshift=0pt]
    %(q_i.south west) -- (q_f.south west) node [black,midway,yshift=-19ex]{$\Gamma$};
  \end{tikzpicture}
  \vspace*{-2.3ex}
  \caption[Definition of a plan with a loop]{Definition of a plan $\Gamma$ with periodic patterns. Stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ containing primitive paths $\varphi_1,\varphi_2,\dots,\varphi_n$ are iterated with a shift $\mathbf{d}$.}
  \vspace*{-1ex}
  \label{fig:state-machine-loop}
\end{figure}

Figure \ref{fig:state-machine-loop} illustrates  the concepts in Definition~\ref{def:primitive}. A plan composed of $n$ stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\varphi_2,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$. $t_1<\dots<t_4$ are time instant $\in\mathbb{R}_{\geq 0}$. $\Gamma_f$ is the accepting stage, indicating the plan is completed, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.

\subsection{Problem formulation}
\label{sec:pbfor}

@@

\begin{pb}[Planning problem]
  \label{pb}
  Consider an initial plan $\Gamma$ in Definition~\ref{def:plan}. The \emph{planning problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
\end{pb}

%The algorithm inputs a user-specified initial plan that consist of different stages. At each stage the plan contains some parameters that allow to alter the path and computations along an energy budget. The alterations are bounded. There is one path constraint set which bounds the path and multiple computation constraint sets, one per each computation parameter, that bound computations. In Figure~\ref{fig:il-abs}, there are two parameters. One relative to the path (\ref{sth:ii}~has a shorter distance between the lines than~\ref{sth:iii}), and the other one to the computations (\ref{sth:i}~processes more images per second than~\ref{sth:ii}).

@@

%Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i}^{\rho}$, or any previous trajectory parameters, propagating the information therein if necessary (see Figure~\ref{fig:state-machine2}).

@@

Appendix~\ref{app:proof-bat} contains a proof of Lemma~\ref{lem:bat}.

>>>>

%% author names and affiliations
\author{
  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, %Henrik Skov Midtiby$^{\text{1}}$, 
  and Ulrik Pagh Schultz$^{\text{1}}$
  %\thanks{This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).}
  \thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
  \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
  \thanks{$^{\text{1}}$A. S. %, H. S. M.,
  and U. P. S. are with the Unmanned Aerial Systems Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense. Email: {\tt\footnotesize ads@mmmi.sdu.dk};} 
  \thanks{$^{\text{2}}$H. G. is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Complutense de Madrid, Spain.}
  \thanks{Digital Object Identifier (DOI): see top of this page.}
}

@@

\begin{abstract}
  The letter presents a planning-scheduling approach for battery-powered autonomous aerial robots, which plans in-flight a coverage path and simultaneously schedules onboard computational tasks. It derives a novel variable coverage motion robust to airborne constraints and an empirically motivated differential periodic energy model. The model is enhanced with the time and energy contribution of the path and tasks, utilizing a previously proposed automatic modeling tool. Accounting for uncertainty, an initial ``plan-schedule'' is replanned and rescheduled in the function of the battery, exploiting all the available resources yet avoiding possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}  %
\label{sec:intro}       %
                        %
\IEEEPARstart{U}{se cases} involving aerial robots span broadly. They compromise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. A typical instance is an aerial robot visiting each point in a given space~\cite{cabreira2019survey}, running some onboard computational tasks, a problem in the literature under coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}. Here, the aerial robot might detect ground patterns and notify other ground-based actors with little human interaction (see Figure~\ref{fig:il-abs}). Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, damage prevention aerial robots~\cite{puri2017agriculture, daponte2019review}. In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}. We refer to computational tasks that can be scheduled with an energy impact as computations. We are interested in the simultaneous energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware planning-scheduling. Generic mobile robotics studies that deal with planning-scheduling energy awareness are scarce~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled} and focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled,ho2019learning}. Yet, aerial robots are particularly affected by various energy considerations. Indeed it would be generally required to land to recharge the battery~\cite{zamanakos2020energy}. Such a state of practice has prompted us to propose a planning-scheduling approach for autonomous aerial robots. It combines the past body of knowledge, addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints. Numerical simulations and experimental data of both static and dynamic plans-schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures. Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies full plan-schedule~(\ref{sth:i}), that is optimized w.r.t. the battery~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).

\begin{figure}[t]
  \centering
  \vspace*{-6.8ex}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,0)
        {\scriptsize \input{\figpath/new/il_abs.tikz}};
    \node[inner sep=0pt] () at (-2,-5.67)
        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
    \node[inner sep=0pt] () at (2.1,-5.67)
        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
  \end{tikzpicture}
  \caption{Illustrative example of planning-scheduling. An initial plan~(in~\ref{sth:i}) is re-planned in-flight computations-wise~(in~\ref{sth:ii}) and motion-wise~(in~\ref{sth:iii}). Follow the collected energy data of a physical aerial robot flying the use case.}
  \label{fig:il-abs}
  \vspace*{-3.7ex}
\end{figure}

@@

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers forward thrust, and control surfaces maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations and vice-versa. The occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2018towards,ho2019learning,ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.

To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (e.g., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc.). Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}. Both the variations trajectories are derived for future time instants employing computations and motion energies and battery models. The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}. The motion wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of various plans-schedules. In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the motion energy model: the evolution is periodic, an observation we exploit in Section~\ref{sec:energy-model} for the computations and motion energies and battery models.

The remaining sections of the letter are then organized as follows. Sec.~\ref{sec:prob} provides basic constructs, such as the concepts of the plan, stages, triggering and final points, and path functions, as well as the problem formulation. Sec.~\ref{sec:algo} describes in detail the methodology of planning-scheduling. Sec.~\ref{sec:experimental} presents the results and showcases the performances, and Sec.~\ref{sec:conclusion} concludes and provides future perspectives. Appendices provide supplementary information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Formulation}  %
\label{sec:prob}               %
                               %
\begin{figure}[t]
  \footnotesize
  \begin{minipage}[l]{0.35\columnwidth}
    \caption{Defs.~\ref{def:plan}--\ref{def:trigs} on a slice of the plan $\Gamma$. $\mathbf{p}_{\Gamma_1},\dots$ are triggering points in which proximity happens change of stages $\Gamma_1,\dots$. Each contains a path function $\varphi_1,\dots$ and parameters to alter the path and schedule $c_{1,1},\dots$.}
    \label{fig:traj1}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.6\columnwidth}
    \centering
    \vspace*{-4.5ex}
    \input{\figpath/new/traj1.tikz}
  \end{minipage}
  \vspace*{-4.5ex}
\end{figure}

Before defining the problem of energy-aware planning-scheduling in Sec.~\ref{sec:pbfor}, Sec.~\ref{sec:prelim} provides necessary preliminaries. For CPP and, e.g., pattern detections in the agricultural use case, we assume that aerial robot travels a \emph{plan} with information about the path and the schedule.

\vspace*{-2ex}
\subsection{Preliminaries}
\label{sec:prelim}

@@

Here, $\Gamma_i$ is a \emph{stage}, and $\mathbb{Z}$ indicates the set of integers. At each stage, the aerial robot travels a path and runs a schedule on the computing hardware. Both are to be altered in Sec.~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}. $\varepsilon_i$ is a stage-dependent value detailed %along with $\mathbf{p}_{\Gamma_i}$ in and 
after Definition~\ref{def:trigs}.

\begin{defn}[Stage]\label{def:stage}
  The $i$th \emph{stage} $\Gamma_i$ at time instant $t$ of a plan $\Gamma$ is
  \begin{equation*}\begin{split}
    \Gamma_i:=\{\varphi_i(\mathbf{p}(t),c_i^\rho),c_i^\sigma\mid
    \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
      &\forall k\in[\sigma]_{>0},\,c_{i,\rho+k}\in\mathcal{S}_{i,k}\,\},
  \end{split}\end{equation*}
  where $c_i^\rho$ and $c_i^\sigma$ are $\rho$ \emph{path} and $\sigma$ \emph{computations parameters}. $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter $c_{i,j}$ constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
\end{defn}

@@

The function $\varphi_i$ is a \emph{path function} specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels %the motion for 
the coverage. The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ indicates the upper/lower bounds of a parameter $\cdot\,$, i.e.,
\begin{equation}
  \underline{\,\cdot\,}\leq\,\cdot\,\leq\overline{\,\cdot\,}.
\end{equation}

%'\>o-O</'

\begin{defn}[Path functions]
  \label{def:paths}
  $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R},\,\forall i\in\{1,2,\dots\}
  $ are \emph{path functions}, forming the path. They are a function of $\mathbf{p}(t)$ and path parameters $c_i^\rho(t)$ and are continuous and twice differentiable.
\end{defn}

@@

The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Def.~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.

Fig.~\ref{fig:traj1} illustrates the concepts in Defs.~\ref{def:plan}--\ref{def:trigs}. $\varphi_0,\dots,\varphi_5$ are path functions. $\varphi_0$ and $\varphi_4$ are circles, while $\varphi_1$, $\varphi_3$, and $\varphi_5$ are lines. They are relative to different stages $\Gamma_1,\Gamma_2,\dots$ but $\Gamma_0$, the stating stage. The constraint sets $\mathcal{C}_{1,1},\mathcal{C}_{2,1},\dots$ forms the area where it is possible to alter the paths $\varphi_1,\varphi_2,\dots$ with the parameters $c_{1,1},c_{2,1},\dots$; the gray area in the figure. %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.

@@

\begin{figure}[h!]
  \footnotesize
  \begin{minipage}[l]{0.75\columnwidth}
    \vspace*{-2.2ex}
    \begin{tikzpicture}[shorten >=.5pt,node distance=12.5ex,on grid,auto,initial text=\hspace*{-3ex}\footnotesize{$\Gamma_0$}]
      \scriptsize
      \node[state,initial] (q_i) {$\Gamma_1$}; 
      \node[state] (q_2) [right=of q_i] {$\Gamma_2$}; 
      \node        [right=of q_2] (q_dots0) {$\cdots$};
      \node[state] (q_0) [right=of q_dots0] {$\Gamma_n$};
      \node[state,accepting] (q_f) [right=of q_0] {$\Gamma_f$};
      \path[->]
      (q_i) edge node {$\mathbf{p}_{\Gamma_{1}}$} (q_2)
      (q_2) edge node {$\mathbf{p}_{\Gamma_{2}}$} (q_dots0)
      (q_dots0) edge node{$\mathbf{p}_{\Gamma_{n-1}}$} (q_0)
      (q_0) edge [bend right=60] node [above] {$\mathbf{p}_{\Gamma_n}$} (q_i)
      (q_i) edge [bend left=-60] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
      (q_2) edge [bend left=-40] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
      (q_0) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
      (q_i) edge [loop above] node {$\mathbf{p}(t_1)$} (q_i)
      (q_2) edge [loop above] node {$\mathbf{p}(t_2)$} (q_2)
      (q_0) edge [loop above] node {$\mathbf{p}(t_3)$} (q_0)
      (q_f) edge [loop above] node {$\mathbf{p}(t_4)$} (q_f)
      ; %end path 
      %\draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=47pt},yshift=0pt]
      %(q_i.south west) -- (q_f.south west) node [black,midway,yshift=-19ex]{$\Gamma$};
    \end{tikzpicture}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.2\columnwidth}
    \centering
    \caption{Plan $\Gamma$ with $n$ primitve stages  in Def~\ref{def:primitive}.}
    \label{fig:state-machine-loop}
  \end{minipage}
  \vspace*{-3.5ex}
\end{figure}
%\begin{figure}[h!]
%  \center
%  \vspace*{-2.2ex}
%  \begin{tikzpicture}[shorten >=.5pt,node distance=12.5ex,on grid,auto,initial text=\hspace*{-3ex}\footnotesize{$\Gamma_0$}]
%    \scriptsize
%    \node[state,initial] (q_i) {$\Gamma_1$}; 
%    \node[state] (q_2) [right=of q_i] {$\Gamma_2$}; 
%    \node        [right=of q_2] (q_dots0) {$\cdots$};
%    \node[state] (q_0) [right=of q_dots0] {$\Gamma_n$};
%    \node[state,accepting] (q_f) [right=of q_0] {$\Gamma_f$};
%    \path[->]
%    (q_i) edge node {$\mathbf{p}_{\Gamma_{1}}$} (q_2)
%    (q_2) edge node {$\mathbf{p}_{\Gamma_{2}}$} (q_dots0)
%    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{n-1}}$} (q_0)
%    (q_0) edge [bend right=60] node [above] {$\mathbf{p}_{\Gamma_n}$} (q_i)
%    (q_i) edge [bend left=-60] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
%    (q_2) edge [bend left=-40] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
%    (q_0) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
%    (q_i) edge [loop above] node {$\mathbf{p}(t_1)$} (q_i)
%    (q_2) edge [loop above] node {$\mathbf{p}(t_2)$} (q_2)
%    (q_0) edge [loop above] node {$\mathbf{p}(t_3)$} (q_0)
%    (q_f) edge [loop above] node {$\mathbf{p}(t_4)$} (q_f)
%    ; %end path 
    %\draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=47pt},yshift=0pt]
    %(q_i.south west) -- (q_f.south west) node [black,midway,yshift=-19ex]{$\Gamma$};
%  \end{tikzpicture}
%  \vspace*{-2.3ex}
%  \caption[Definition of a plan with a loop]{Definition of a plan $\Gamma$ with periodic patterns. Stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ containing primitive paths $\varphi_1,\varphi_2,\dots,\varphi_n$ are iterated with a shift $\mathbf{d}$.}
%  \vspace*{-1ex}
%  \label{fig:state-machine-loop}
%\end{figure}

Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Def.~\ref{def:primitive}. A plan composed of $n$ stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\varphi_2,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$. $t_1<\dots<t_4$ are time instant $\in\mathbb{R}_{\geq 0}$. $\Gamma_f$ is the accepting stage, indicating the plan is completed, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.

\vspace*{-2ex}
\subsection{Problem formulation}
\label{sec:pbfor}

@@

\begin{pb}[Planning problem]
  \label{pb}
  Consider an initial plan $\Gamma$ in Def.~\ref{def:plan}. The \emph{planning problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
\end{pb}

%The algorithm inputs a user-specified initial plan that consist of different stages. At each stage the plan contains some parameters that allow to alter the path and computations along an energy budget. The alterations are bounded. There is one path constraint set which bounds the path and multiple computation constraint sets, one per each computation parameter, that bound computations. In Fig.~\ref{fig:il-abs}, there are two parameters. One relative to the path (\ref{sth:ii}~has a shorter distance between the lines than~\ref{sth:iii}), and the other one to the computations (\ref{sth:i}~processes more images per second than~\ref{sth:ii}).

@@

%Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i}^{\rho}$, or any previous trajectory parameters, propagating the information therein if necessary (see Fig.~\ref{fig:state-machine2}).

@@

Appendix~\ref{app:proof-bat} contains a proof of Lem.~\ref{lem:bat}.
